

\subsubsection*{API}

A set of routine definitions, protocols, and tools for building software and applications. An API specification can take many forms, but often include specifications for routines, data structures, object classes, or variables.

\subsubsection*{AR}

Augmented reality is the integration of digital information with the user's environment in real time. Unlike virtual reality, which creates a totally artificial environment, augmented reality uses the existing environment and overlays new information on top of it.

\subsubsection*{CSRF}

Cross-site request forgery, also known as one-click attack or session riding and abbreviated as CSRF or XSRF, is a type of malicious exploit of a website where unauthorized commands are transmitted from a user that the web application trusts.\cite{Ristic2005}

\subsubsection*{Function as a Service}

Function as a service (FaaS) is a category of cloud computing services that provides a platform allowing customers to develop, run, and manage application functionalities without the complexity of building and maintaining the infrastructure typically associated with developing and launching an app.\cite{roberts_2018}

\subsubsection*{GPS}

The Global Positioning System (GPS), originally Navstar GPS, is a satellite-based radio navigation system owned by the United States government and operated by the United States Air Force.[2] It is a global navigation satellite system that provides geolocation and time information to a GPS receiver anywhere on or near the Earth where there is an unobstructed line of sight to four or more GPS satellites.

\subsubsection*{GUI}

A graphical user interface utilizes the graphical capabilities of a computer to provide a
user interface for computer software. GUIs often employ images, symbols and visual cues
to facilitate user interaction in a point-and-click manner. Common methods for providing
user input include the use of keyboards, mice, pen devices, touch screens or other devices
for physical interaction.

\subsubsection*{Open Source Software}

Open Source Software (OSS) is software distributed with a license allowing access to its
source code, free redistribution, the creation of derived works, and unrestricted use.
